Simulation with algorithm 2- different means and one nuisance granularity

### 2021-08-12 sim_setup_algo2_diffmeans.Rmd
adding the handpicking examples

---
title: "Simulation with algorithm 2"
author: "Sayani Gupta"
output: pdf_document
---

@@

Three circular granularities g1, g2 and g3 are considered with levels 2, 3 and 4 respectively. Many time series with 600 observations are created using the five designs below, each of which is iterated four times. We anticipate to have five clusters, each with four time series conforming to the same design, once we execute the clustering.

@@

```{r tab-gran}
design = c("design-1", "design-2", "design-3", "design-4", "design-5")
g1 = c("no", "yes" , "no", "yes", "yes")
g2 = c("no", "no" , "yes", "no", "yes")
g3 = c("no", "yes" , "no", "yes", "yes")
table <- tibble(design, g1, g2, g3) %>% kable()
table
```

@@

@@

set.seed(12345)
data_design_1 <- generate_design(t = 599, mu = 0)
data_design_2 <- generate_design(t = 599, mu = c(0, 2))
data_design_3 <- generate_design(t = 599, mu = c(0, 2, 4))
data_design_4 <- generate_design(t = 599, mu = c(0, 2, 4, 6))
data_design_5 <- generate_design(t = 599, mu = c(0, 2, 4, 6, 8, 10))
```

@@

# Raw plots
```{r all-design}
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4,data_design_5, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))

@@

```{r}
seed_len = seq(12345, 12348, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_design_2 <- generate_design(t = 599, mu = c(0, 2))
data_design_3 <- generate_design(t = 599, mu = c(0, 2, 4))
data_design_4 <- generate_design(t = 599, mu = c(0, 2, 4, 6))
data_design_1 <- generate_design(t = 599, mu = 0)
data_design_5 <- generate_design(t = 599, mu = c(0, 2, 4, 6, 8, 10))
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4,data_design_5, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))
}) %>% bind_rows(.id = "seed_id")

@@

write_csv(data_wpd, "data_wpd.rds")
```

@@

```{r}
  groups <- cutree(hc, k=5) %>% as_tibble() %>% 
mutate(data_id = data_wide$data_id) %>% rename("group" = "value")

# With optimal number of clusters

Design 2 and 4 form a part of the same cluster with the optimal number of clusters chosen as 4. Design 2 and 4 are similar in the sense that both of them changes across categories for g1 and g3, and remains constant for g2.

```{r}
  groups <- cutree(hc, k=koptimal) %>% as_tibble() %>% 
mutate(data_id = data_wide$data_id) %>% rename("group" = "value")

@@

```{r}
pc <- prcomp(data_wide_group[c(2, 3, 4)], center = F, scale = F)

@@

>>>>

---
title: "Simulation with algorithm 2- different means and one nuisance granularity"
author: "Sayani Gupta"
output: pdf_document
---

@@

Three circular granularities g1, g2 and g3 are considered with levels 2, 3 and 4 respectively. Many time series with 600 observations are created using the four designs below, each of which is iterated five times. We anticipate to have four clusters, each with five time series conforming to the same design, once we execute the clustering.

@@

@@

g1 = rep(c(0, 1), length.out= length(t))
g1_dist_design1 <- rep(c(0, 0), length.out= length(t))
g1_dist_design2 <- rep(c(0, 2), length.out= length(t))
g1_dist_design3 <- rep(c(1, 4), length.out= length(t))
g1_dist_design4 <- rep(c(2, 4), length.out= length(t))

g2 = rep(c(0, 1, 2), length.out= length(t))
g2_dist_design1 <- rep(c(0, 0, 0), length.out= length(t))
g2_dist_design2 <- rep(c(1, 5, 7), length.out= length(t))
g2_dist_design3 <- rep(c(1, 2, 3), length.out= length(t))
g2_dist_design4 <- rep(c(0, 2, 4), length.out= length(t))

g3 = rep(c(0, 1, 2, 3), length.out= length(t))
g3_dist_design1 <- rep(c(0, 0, 0, 0), length.out= length(t))
g3_dist_design2 <- rep(c(0, 0, 0, 0), length.out= length(t))
g3_dist_design3 <- rep(c(0, 0, 0, 0), length.out= length(t))
g3_dist_design4 <- rep(c(0, 0, 0, 0), length.out= length(t))

time_series <- bind_rows(
  bind_cols(t, g1, g2, g3, g1_dist_design1, g2_dist_design1, g3_dist_design1),
  bind_cols(t, g1, g2, g3,  g1_dist_design2, g2_dist_design2, g3_dist_design2),
  bind_cols(t,  g1, g2, g3, g1_dist_design3, g2_dist_design3, g3_dist_design3),
  bind_cols(t,  g1, g2, g3, g1_dist_design4, g2_dist_design4, g3_dist_design4), .id = "design") %>%
  set_names(c("design", "t", "g1", "g2", "g3", "g1_dist", "g2_dist", "g3_dist")) %>% 
  mutate(sum_dist = g1_dist + g2_dist + g3_dist)

 time_series %>% group_by(design) %>% summarize(s = unique(sum_dist))
```

```{r}

@@

set.seed(12345)
data_design_1 <- generate_design(t = 299, mu = 0)
data_design_2 <- generate_design(t = 299, mu = c(1, 7, 7, 3, 5, 9))
data_design_3 <- generate_design(t = 299, mu = c(2, 6, 4, 5, 3, 7))
data_design_4 <- generate_design(t = 299, mu = c(2, 6, 6, 4, 4, 8))
```

@@

# Raw plots
```{r all-design}
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))

@@

```{r}
seed_len = seq(12345, 12399, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_design_1 <- generate_design(t = 299, mu = 0)
data_design_2 <- generate_design(t = 299, mu = c(1, 7, 7, 3, 5, 9))
data_design_3 <- generate_design(t = 299, mu = c(2, 6, 4, 5, 3, 7))
data_design_4 <- generate_design(t = 299, mu = c(2, 6, 6, 4, 4, 8))
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))
}) %>% bind_rows(.id = "seed_id")

@@

#write_csv(data_wpd, "data_wpd.rds")
```

@@

```{r}
  groups <- cutree(hc, k=4) %>% as_tibble() %>% 
mutate(data_id = data_wide$data_id) %>% rename("group" = "value")

@@

```{r, eval = FALSE}
pc <- prcomp(data_wide_group[c(2, 3, 4)], center = F, scale = F)

@@

```{r}
data_plot <- left_join(data_wide_group,  bind_data_iter %>% distinct(design, data_id)) %>%
  mutate(pred_group = case_when(
    group == 1 ~"design-1",
    group == 2 ~"design-2",
    group == 3 ~"design-3",
    group == 4 ~"design-4"
  )) %>% 
  mutate(pred_group = as.factor(pred_group),
         design = as.factor(design)
  )

xtab <- confusionMatrix(data_plot$design, data_plot$pred_group)

data_plot %>%  ggplot(aes(x=g1, y=g2)) + geom_point(aes(colour = design)) +
  scale_color_brewer(palette = "Dark2")

left_join(data_wide_group,  bind_data_iter %>% distinct(design, data_id)) %>%  ggplot(aes(x=g1, y=g3)) + geom_point(aes(colour = design)) +
  scale_color_brewer(palette = "Dark2")

left_join(data_wide_group,  bind_data_iter %>% distinct(design, data_id)) %>%  ggplot(aes(x=g2, y=g3)) + geom_point(aes(colour = design)) +
  scale_color_brewer(palette = "Dark2")
